R Packages to Aid in Handling Web Access Logs

### 2015-12-26 paper/paper.Rmd
start iptools section

>>>>

Working with these values allows an analyst to validate their data (by checking for false or spoof addresses) and is a necessary prerequisite to the use of some IP geolocation systems (covered later) which require the numeric forms of IP addresses (\samp{3232235521}) rather than the standard \dfn{dotted-decimal} form (\samp{192.168.0.1}) found in access logs.

Based around the \emph{Boost ASIO} C++ library \citep{boostcite}, \pkg{iptools} is a package designed for this kind of IP manipulation (and more). Designed around combined code, it is extremely fast (for that code that does not rely on internet connections) and boasts a range of features.

One of the most crucial is \code{ip\_classify}, which, when provided with a vector of IP addresses, identifies whether they follow the IPv4 or IPv6 standard. As a side-effect of this, it can be used to identify if IP addresses are invalid, or spoofed, prior to further work based on the assumption that they are correct:

```{r, eval=TRUE}
# Load iptools and construct a vector of IPs
library(iptools)
ip_addresses <- c("192.168.0.1", "2607:f8b0:4006:80b::1004", "Chewie")
ip_classify(ip_addresses)

### 2015-12-26 paper/paper.tex
start iptools section

>>>>

Working with these values allows an analyst to validate their data (by
checking for false or spoof addresses) and is a necessary prerequisite
to the use of some IP geolocation systems (covered later) which require
the numeric forms of IP addresses (\samp{3232235521}) rather than the
standard \dfn{dotted-decimal} form (\samp{192.168.0.1}) found in access
logs.

Based around the \emph{Boost ASIO} C++ library \citep{boostcite},
\pkg{iptools} is a package designed for this kind of IP manipulation
(and more). Designed around combined code, it is extremely fast (for
that code that does not rely on internet connections) and boasts a range
of features.

One of the most crucial is \code{ip\_classify}, which, when provided
with a vector of IP addresses, identifies whether they follow the IPv4
or IPv6 standard. As a side-effect of this, it can be used to identify
if IP addresses are invalid, or spoofed, prior to further work based on
the assumption that they are correct:

\begin{Schunk}
\begin{Sinput}
# Load iptools and construct a vector of IPs
library(iptools)
ip_addresses <- c("192.168.0.1", "2607:f8b0:4006:80b::1004", "Chewie")
ip_classify(ip_addresses)
\end{Sinput}
\begin{Soutput}
#> [1] "IPv4"    "IPv6"    "Invalid"
\end{Soutput}
\end{Schunk}
